---
title: "cancerEDA.rmd"
output: html_notebook
---
# 1.1 Load libraries and data files
```{r}
knitr::opts_chunk$set(echo = TRUE)

library('ggplot2') # visualization
library('ggthemes') # visualization
library('scales') # visualization
library('grid') # visualisation
library('gridExtra') # visualisation
library('corrplot') # visualisation
library('ggfortify') # visualisation
library('ggraph') # visualisation
library('igraph') # visualisation
library('dplyr') # data manipulation
library('readr') # data input
library('tibble') # data wrangling
library('tidyr') # data wrangling
library('stringr') # string manipulation
library('forcats') # factor manipulation
library('tidytext') # text mining
library('SnowballC') # text analysis
library('wordcloud') # test visualisation
```

Reading in the variants data tables:

```{r}
train <- read_csv('input/training_variants')
test  <- read_csv('input/test_variants')
```

Reading in the text files currently takes a bit more effort in R. The previous read-in method didn¡¯t work properly. Use this one instead:

```{r}
train_txt_dump <- tibble(text = read_lines('input/training_text', skip = 1))
train_txt <- train_txt_dump %>%
  separate(text, into = c("ID", "txt"), sep = "\\|\\|")
train_txt <- train_txt %>%
  mutate(ID = as.integer(ID))

test_txt_dump <- tibble(text = read_lines('../input/test_text', skip = 1))
test_txt <- test_txt_dump %>%
  separate(text, into = c("ID", "txt"), sep = "\\|\\|")
test_txt <- test_txt %>%
  mutate(ID = as.integer(ID))

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
